---
title: "PML project"
author: "Haoyu Wang"
date: "March 23, 2019"
output: html_document
---
This is the Rmd of the PML class project.

load the data into traning and testing sets

```{r}
library(caret)
set.seed(1)
training <- read.csv("pml-training.csv", na.strings = c("NA", ""))
testing <- read.csv("pml-testing.csv", na.strings = c("NA", ""))
```

After looking at the data, there are many coloums with all NA's so we get rid of them.

```{r}
training <- training[, colSums(is.na(training)) == 0]
testing <- testing[, colSums(is.na(testing)) == 0]
```

Also get rid of their names and other columns which aren't useful for prediction. 

```{r}
trainData <- training[, -c(1:7)]  
testData <- testing[, -c(1:7)]
```

Create validation set to estimate the out of sample error.
```{r}
inTrain <- createDataPartition(trainData$classe, p = 0.7, list = FALSE)
train <- trainData[inTrain, ]
valid <- trainData[-inTrain, ]
```


Train using random forest with cross validation of 4 fold.
```{r}
ctrl <- trainControl(method = "cv",number=4)
mod_rf <- train(classe ~ ., data = train, method = "rf", trControl = ctrl)
```


Predict using valid data set.

```{r}
predict_rf <- predict(mod_rf, valid)
```
compare with classe data in the validation set.


```{r}
compare <- confusionMatrix(valid$classe, predict_rf)
print(compare)
```
Using our model to predict the classe for test data.
```{r}
result <- predict(mod_rf, testData)
print(result)
```

